---
title: "HW7"
author: "linshuangquan"
date: "2017年5月6日"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#No.3

##a
```{r}
x1 = c(3, 2, 4, 1, 2, 4, 4)
x2 = c(4, 2, 4, 4, 1, 3, 1)
y = c(rep("red",4),rep("blue",3))
plot(x1, x2, col = y)
```

##b

It is easy to find that the support vectors are (2,2),(2,1),(4,4),(4,3).Thus:           
\[a=\frac{3.5-1.5}{4-2}=1\]
\[b=1.5-2*a=-0.5\]
The optimal separating hyperplane is $x_1-x_2-0.5=0$
```{r}
plot(x1, x2, col = y)
abline(-0.5, 1)

```

##c

$\beta_0=0.5,\beta_1=-1,\beta_2=1$
When $0.5-x_1+x_2>0$,y="red",when$0.5-x_1+x_2<0$,y="blue".

##d
```{r}
plot(x1, x2, col = y)
abline(-0.5, 1)
abline(-1, 1, lty = 2)
abline(0, 1, lty = 2)
```

##e
The support vectors are (2,2),(2,1),(4,4),(4,3).

##f

A slight movement of observation #7 (4,1) blue would not have an effect on the maximal margin hyperplane since its movement would be outside of the margin.

##g
```{r}
plot(x1, x2, col=y)
abline(-0.8, 1)
```

This hyperplane: $x_1-x_2-0.8=0$.

##h
```{r}
plot(x1,x2,col=y)
points(4,2,col="red")
```


#No.7

##a
```{r}
library(ISLR)
Auto$level <- as.factor(ifelse(Auto$mpg>median(Auto$mpg),1,0))
Auto$mpg <- NULL
```

##b
```{r}
library(e1071)
set.seed(1234)
fit.model = tune(svm, level ~ ., data = Auto, kernel = "linear", ranges = list(cost = c(0.01, 
    0.1, 1, 10, 100,1000)))
summary(fit.model)
```
When cost=1 we get the minimum error rate.

##c
```{r}
set.seed(123)
fit.poly = tune(svm, level ~ ., data = Auto, kernel = "polynomial", ranges = list(cost = c(0.1, 
    1, 10,100), degree = c(2, 3, 4)))
summary(fit.poly)
fit.poly$best.parameters
set.seed(456)
fit.radial = tune(svm, level ~ ., data = Auto, kernel = "radial", ranges = list(cost = c(0.1, 
    1,10,100), gamma = c(0.01, 0.1, 1, 10, 100)))
summary(fit.radial)
fit.radial$best.parameters
```

##d
```{r}
svm.linear = svm(level ~ ., data = Auto, kernel = "linear", cost = 1)
svm.poly = svm(level ~ ., data = Auto, kernel = "polynomial", cost = 100, 
    degree = 2)
svm.radial = svm(level ~ ., data = Auto, kernel = "radial", cost = 10, gamma = 0.1)

plotpairs = function(fit) {
        index <- combn(names(Auto)[1:7],2)
        for(i in 1:ncol(index)){
                plot(fit, Auto, as.formula(paste(index[1,i],"~", index[2,i], sep = "")))
        }
}

plotpairs(svm.linear)
plotpairs(svm.poly)
plotpairs(svm.radial)


```