---
title: "HW3"
author: "linshuangquan"
date: "2017年3月18日"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## No.8

###a
```{r}
set.seed(1)
x <- rnorm(100)
y <- x-2*x^2+rnorm(100)
```
In this case,n=100,p=2.the equation form:
\[y_t=x_t-2x_t^2+\epsilon_t\]

###b
```{r}
plot(x,y)
```
There is nonlinear relationship betwwen x and y.

###c
```{r}
library(glmnet)
library(boot)
dat <- data.frame(x,y)
cv.error <- rep(NA,4)
for(i in 1:4){
        glm.fit <- glm(y~poly(x,i),data = dat)
        cv.error[i] <- cv.glm(dat,glm.fit)$delta[1]
}
names(cv.error) <- 1:4
cv.error
```
When p=2, the fit is best.

###d
```{r}
set.seed(2)
cv.error2 <- rep(NA,4)
for(i in 1:4){
        glm.fit <- glm(y~poly(x,i),data = dat)
        cv.error[i] <- cv.glm(dat,glm.fit)$delta[1]
}
names(cv.error) <- 1:4
cv.error2
```
The result is the same, because LOOCV will be the same since it evaluates n folds of a single observation.

###e

The polynomial of 2 has the lowest LOOCV error. Because the data are generated from quadratic equation.

###f

```{r}
summary(glm(y~poly(x,4),data = dat))
```
We can see that the p-value of poly of 3 and 4 are insignificant, which agree with cross-validation results.



##No.9

###a

```{r}
library(MASS)
attach(Boston)
mu <- mean(medv)
mu
```

###b

```{r}
se <- sd(medv)/(sqrt(length(medv)))
se
```

###c
```{r}
boot.fn <- function(data,index){
        return(mean(data[index]))
}

mu_boot <- boot(medv, boot.fn, 1000)
mu_boot
```

###d
The confidence interval of bootstrap:
```{r}
c(mu_boot$t0-1.96*0.4135401,mu_boot$t0+1.96*0.4135401)
t.test(medv)$conf.int
```

###e
```{r}
med <- median(medv)
```

###f
```{r}
boot.fn2 <- function(data,index){
        return(median(data[index]))
}
med_boot <- boot(medv,boot.fn2,1000)
med_boot
```
Thus the bootstrap standard error of median is 0.3858694.

###g

```{r}
quan_1 <- quantile(medv,0.1)
```

###h
```{r}
boot.fn3 <- function(data,index){
        return(quantile(data[index],0.1))
}
quan_boot <- boot(medv,boot.fn3,1000)
quan_boot
```
The standard error is 0.5148446.
